Hybrid platforms and bargaining power

### 2023-12-13 src/paper/application.tex
Relax investment cost assumption (make it weakly convex)

Let us now turn to the determination of the equilibrium number of fringe firms.
Assume that there is an unlimited number of potential fringe entrants, indexed by $i \in \mathbb{R}^+_0$.
In the first stage of the game, each fringe firm must create a viable product at an investment cost $I_F > 0$.
In the second stage, firms that made this investment plus the platform engage in producing and selling their respective products.
If there are $N_F$ fringe entrants along with $N_P$ platform products and $N_C$ consumers, then, as discussed previously, the total value they create together is given by $\Pi(N_P, N_F, N_C) = N_C f(N_P, N_F)$.
Finally, the platform and the entrants share this profit according to the profit sharing rule from \cref{ass:profit_sharing} or \cref{ass:profit_sharing_two_sided}, and the fringe gets $\pi_F(N_P, N_F, N_C)$.

The equilibrium number of entrants is determined by a free entry condition: in the end, the fringe firms' total profits should be equal to the aggregated investment cost.
\begin{definition}
    \label{ass:free_entry}
    Let us define a free entry equilibrium by the following conditions:
    \begin{itemize}
        \item Profits are shared according to \cref{ass:profit_sharing} or \cref{ass:profit_sharing}.
        \item Entrants make zero profits: $\pi_F(N_P, N_F) = I_F N_F$ after accounting for entry costs.
    \end{itemize}
\end{definition}

@@

        \draw[name path=piF,domain=0.01:5.5,variable=\x,black,thick] plot ({\x},{8*((\x)/(0.3+\x))-8*((\x-0.3*ln(\x+0.3)-0.361)/(\x))});
        \draw[name path=IF,domain=0.01:5.5,variable=\x,black,dashed,thick] plot ({\x},{(\x)/3});
        \node[anchor=north east] at (5,1) {$\pi_F(N_P, N_F, N_C)$};
        \node[anchor=south east] at (5,5/3) {$I_F N_F$};

@@

        \node[anchor=south] at (5,1) {$\pi_F(N_P, N_F, N_C)$};
        \node[anchor=north] at (5,0.6) {$\pi_F(N_P', N_F, N_C)$};
        \node[anchor=south east] at (5,5/3) {$I_F n_F$};

@@

The participants negotiate over the aggregate profits that they can achieve in the subsequent period (assuming non-collusive, monopolistic pricing, as before).
I assume that bargaining outcomes are determined according to \cref{ass:profit_sharing}, where $f(N_P, N_F)$ is defined as the total profits that the platform and the entrants can achieve by selling their products.
From \cref{eq:optimal_profit}, the total profit achieved by the platform and $N_F$ fringe firms is given by
\begin{align*}
    f(N_P, N_F) = \mu \frac{n V_F + N_P V_P}{n V_F + N_P V_P + 1}.
\end{align*}
This yields the following closed-form expressions for the total profits of the participants.
\begin{proposition}
    \label{prop:platform_profits_bargaining}
    The platform's total profits are
    \begin{align*}
        \pi^t_P &=\int_0^1 f(N_P, sN_F) \ds \\
                &= \mu \left[ 1 - \frac{\log \left(1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} \right].
    \end{align*}
    The total profits of the whole fringe is given by
    \begin{align*}
        \pi^t_F = \mu \left[ \frac{\log \left( 1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} - \frac{1}{N_P V_P + N_F V_F + 1} \right] - I_F N_F.
    \end{align*}
\end{proposition}

@@

\begin{lemma}
    \label{lem:slope_at_eq}
    Let the conditions in \cref{ass:single_crossing} hold. Then for any $N_F^* > 0$ for which $\pi_F(N_P, N_F^*) = I_F$, the partial derivative with respect to the number of fringe firms is smaller than the investment cost:
    \begin{align*}
        \left. \frac{\partial \pi_F(N_P, N_F)}{\partial N_F} \right|_{N_F = N_F^*} < I_F.
    \end{align*}
\end{lemma}
\begin{proof}[Proof of \cref{lem:slope_at_eq}]
    \cref{ass:single_crossing} states that at any $N_F \geq 0$, $\pi_F(N_P, N_F)$ is either concave or decreasing.
    In the remainder, for ease of notation drop $N_C$ from the arguments of $\pi_F$ profit function as it is simply a multiplicative constant, and let us denote partial derivatives as follows:
    \begin{align*}
        \partial_F \pi_F(N_P^*, N_F^*) \coloneqq \left. \frac{\partial \pi_F(N_P, N_F)}{\partial N_F} \right|_{N_P = N_P*, N_F = N_F^*}.
    \end{align*}

    Notice that the fact that $\pi_F$ is concave or decreasing in $N_F$ implies that if $\partial_F \pi_F(N_P, N_F')$ for some $N_F' \geq 0$, then $\partial_F \pi_F(N_P, N_F'') < \partial_F \pi_F(N_P, N_F')$ for any $\tilde{N_F} < \bar{N_F}$.

    Next, observe that if $\partial_F \pi_F(N_P, 0) < I_F$, then there is no equilibrium with $N_F > 0$.
    To show this, assume by contradiction that $\exists N_F^* > 0$ such that $\pi_F(N_P, N_F^*) = I_F N_F^*$.
    Then the mean value theorem implies that there is a $\bar{N}_F \in (0, N_F^*)$ such that $\partial_F \pi_F(N_P, \bar{N}_F) = I_F$.
    However, this clearly cannot be the case as $\partial_F \pi_F(N_P, N_F) < I_F$ for all $N_F > 0$.

    Now let $N_F^*$ be a positive number for which $f(N_P, N_F^*) = I_F N_F^*$, if it exists.
    It is easy to see that $\partial \pi(N_P, N_F^*) < I_F$.
    The reason is that if it exists, then $\partial_F \pi_F(N_P, 0) > I_F$.
    Now if $\partial_F \pi_F(N_P, N_F^*) \geq I_F \forall N_F > 0$, then $f(N_P, N_F) > I_F N_F$, and the two functions do not intersect.
    Therefore, there must exist some $\bar{N}_F > 0$ for which $\partial_F \pi_F(N_P, \bar{N}_F) < I_F$.
    This in turn implies that $\partial_F \pi_F(N_P, N_F) \leq \partial_F \pi_F(N_P, \bar{N}_F) < I_F$ for all $N_F > \bar{N}_F$.
\end{proof}

\begin{proof}[Proof of \cref{prop:unique_equilibrium}]
    \Cref{lem:slope_at_eq} states that for any positive $N_F^*$ for which $\pi_F(N_P, N_F^*)$, the partial derivative with respect to the number of fringe firms is negative.
    Now assume by contradiction that $\exists 0 < N_F^* < N_F^{**}$ such that $\pi_F(N_P, N_F^*) = I_F N_F^*$ and $\pi_F(N_P, N_F^{**}) = I_F N_F^{**}$.
    But then the mean value theorem implies that there is a $\bar{N}_F \in (N_F^*, N_F^{**})$ such that $\partial_F \pi_F(N_P, \bar{N}_F) = I_F$.
    This is a contradiction, as $\partial_F \pi_F(N_P, N_F) < I_F$ for all $N_F^* < N_F$.
\end{proof}

@@

\begin{proof}[Proof of \cref{cor:fringe_entry}]
    \Cref{prop:unique_equilibrium} establishes that if an equilibrium with $N_F > 0$ exists, it is unique.
    Use the implicit function theorem on the equation from \cref{ass:free_entry} to obtain
    \begin{align*}
        \frac{\partial N_F}{\partial N_P} = \frac{\frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_P}}{I_F - \frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F}}
    \end{align*}
    The derivative exists if the above expression is well-defined, i.e. $\frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F} \neq I_F$.
    Remember from \cref{prop:share_of_fringe} that the numerator of this expression is negative under the condition $\frac{\partial^2 f(N_P, N_F, N_C)}{\partial N_P \partial N_F}$.
    Now all we need to show to conclude the proof is that
    \begin{align*}
        \frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F} < I_F,
    \end{align*}
    which is the statement of \cref{lem:slope_at_eq}.
\end{proof}

\begin{proof}[Proof of \cref{prop:aggregate_size_additive}]
    Assume by contradiction that $\frac{\partial N_F^*}{\partial N_P} \geq -\frac{\alpha}{\beta}$ for some $N_P'$.
    Then, for $\forall K > 0$, $\exists \Delta \in (0, K)$ such that $N_F^*(N_P' + \Delta) \geq N_F^*(N_P') - \frac{\alpha}{\beta}\Delta$. For ease of notation, let us denote $N_P'' = N_P' + \Delta$, $N_F' = N_F^*(N_P')$ and $N_F'' = N_F^*(N_P'')$.

    First, let us show that fringe profits are lower than total investment costs if $\bar N_F = N_F^*(N_P') - \frac{\alpha}{\beta}\Delta$.
    In order to do this, consider the following formulation of the fringe profit function:
    \begin{align*}
        \pi_F(N_P', N_F', N_C) &= \int_0^1 w(t) \frac{\Pi(N_P, t N_F, N_C)}{\partial t} \dt \\
        &= N_C \int_0^1 w(t) \underbrace{\frac{\partial}{\partial t}g(\alpha N_P + \beta t N_F)}_{\coloneq D(N_P, N_F)} \dt,
    \end{align*}
    where $w(t) = t$ or $w(t) = t^2$ in the one-sided and two-sided bargaining cases, respectively.

    Let us focus on the term $D(N_P, N_F)$.
    First, calculate
    \begin{align*}
        D(N_P', N_F') = \beta N_F' g'(\alpha N_P' + \beta t N_F').
    \end{align*}
    Let us do the same for $D(N_P'', \bar{N}_F) = D(N_P' + \Delta, N_F - \frac{\alpha}{\beta} \Delta)$ to get
    \begin{align*}
        D(N_P'', \bar{N}_F) = \beta \bar{N}_F g'(\alpha N_P' + \beta t N_F' + \underbrace{\Delta \alpha (1-t)}_{> 0}).
    \end{align*}
    Substitute these expressions into $\pi_F$ to get
    \begin{align*}
        \pi_F(N_P', N_F', N_C) &= N_C N_F' \beta \int_0^1 w(t) g'(\alpha N_P' + \beta t N_F') \dt, \\
        \pi_F(N_P'', \bar{N}_F, N_C) &= N_C \bar{N}_F \beta \int_0^1 w(t) g'(\alpha N_P' + \beta t N_F' + \Delta \alpha (1-t)) \dt.
    \end{align*}
    Finally, let us bound the difference between $\pi_F(N''_Pm \bar{N}_F) - I_F \bar{N}_F$ from above:
    \begin{align*}
        \pi_F(N_P'', \bar{N}_F, N_C) - I_F \bar{N}_F &= \frac{\bar{N}_F}{N_F'}\left[\beta N_C \int_0^1 w(t) g'(\alpha N_P' + \beta t N_F' + \Delta \alpha (1-t)) \dt - I_F N_F' \right] \\
        &< \frac{\bar{N}_F}{N_F'}\left[\beta N_C \int_0^1 w(t) g'(\alpha N_P' + \beta t N_F') \dt - I_F N_F' \right] \\
        &= \frac{\bar{N}_F}{N_F'}\left[ \pi_F(N_P', N_F', N_C) - I_F N_F \right] \\
        &= 0.
    \end{align*}
    The inequality is due to the concavity of $g$, and the final equality is the result of profits being zero in the equilibrium $(N_P', N_F', N_C)$.

    All that remains to be shown is that $\pi_F(N_P'', N_F'', N_C) < N_F'' I_F$.
    This is a consequence of the fact that, under \cref{ass:single_crossing}, $\pi_F$ is either concave or decreasing in $N_F$.
    Therefore, if it at some point ($\bar{N}_F$) dips below the linear function $N_F \mapsto I_F N_F$, it can never reach it again for any $N_F'' > \bar{N}_F$.
    With this we arrive at a contradiction, as $(N_P'', N_F'', N_C)$ cannot be an equilibrium.

    Therefore, the initial assumption that $\frac{\partial N_F^*}{\partial N_P} \geq -\frac{\alpha}{\beta}$ was wrong.
    As we have from \cref{cor:fringe_entry} that $\frac{\partial N_F^*}{\partial N_P}$ exists, it must be the case that
    \begin{align*}
        \frac{\partial N_F^*}{\partial N_P} < -\frac{\alpha}{\beta}.
    \end{align*}

>>>>

Let us now turn to the determination of the equilibrium number of fringe firms.
Assume that there is an unlimited number of potential fringe entrants, indexed by $i \in \mathbb{R}^+_0$.
In the first stage of the game, each fringe firm must create a viable product at some investment cost.
Let us denote the total investment costs of $N_F$ fringe firms by $I_F(N_F)$.
\begin{assumption}
    Assume that $I_F(N_F)$ is a strictly increasing, convex, twice differentiable function:
    \begin{align*}
        \frac{\partial I_F(N_F)}{\partial N_F} > 0, \quad \frac{\partial^2 I_F(N_F)}{\partial N_F^2} \geq 0.
    \end{align*}
\end{assumption}
This assumption essentially states that the marginal investment cost of the fringe is increasing in the number of fringe firms.
Notice that this only assumes weak convexity, and thus includes the case of constant marginal investment costs.

In the second stage, firms that made this investment plus the platform engage in producing and selling their respective products.
If there are $N_F$ fringe entrants along with $N_P$ platform products and $N_C$ consumers, then, as discussed previously, the total value they create together is given by $\Pi(N_P, N_F, N_C) = N_C f(N_P, N_F)$.
Finally, the platform and the entrants share this profit according to the profit sharing rule from \cref{ass:profit_sharing} or \cref{ass:profit_sharing_two_sided}, and the fringe gets $\pi_F(N_P, N_F, N_C)$.

The equilibrium number of entrants is determined by a free entry condition: in the end, the fringe firms' total profits should be equal to the aggregated investment cost.
\begin{definition}
    \label{ass:free_entry}
    Let us define a free entry equilibrium by the following conditions:
    \begin{itemize}
        \item Profits are shared according to \cref{ass:profit_sharing} or \cref{ass:profit_sharing}.
        \item Entrants make zero profits: $\pi_F(N_P, N_F) = I_F(N_F)$ after accounting for entry costs.
    \end{itemize}
\end{definition}

@@

        \draw[name path=piF,domain=0.01:5.5,variable=\x,black,thick] plot ({\x},{8*((\x)/(0.3+\x))-8*((\x-0.3*ln(\x+0.3)-0.361)/(\x))});
        \draw[name path=IF,domain=0.01:5.5,variable=\x,black,dashed,thick] plot ({\x},{(\x)/3});
        \node[anchor=north east] at (5,1) {$\pi_F(N_P, N_F, N_C)$};
        \node[anchor=south east] at (5,5/3) {$I_F(N_F)$};

@@

        \node[anchor=south] at (5,1) {$\pi_F(N_P, N_F, N_C)$};
        \node[anchor=north] at (5,0.6) {$\pi_F(N_P', N_F, N_C)$};
        \node[anchor=south east] at (5,5/3) {$I_F(N_F)$};

@@

The participants negotiate over the aggregate profits that they can achieve in the subsequent period (assuming non-collusive, monopolistic pricing, as before).
I assume that bargaining outcomes are determined according to \cref{ass:profit_sharing}, where $f(N_P, N_F)$ is defined as the total profits that the platform and the entrants can achieve by selling their products.
From \cref{eq:optimal_profit}, the total profit achieved by the platform and $N_F$ fringe firms is given by
\begin{align*}
    f(N_P, N_F) = \mu \frac{n V_F + N_P V_P}{n V_F + N_P V_P + 1}.
\end{align*}
This yields the following closed-form expressions for the total profits of the participants.
\begin{proposition}
    \label{prop:platform_profits_bargaining}
    The platform's total profits are
    \begin{align*}
        \pi^t_P &=\int_0^1 f(N_P, sN_F) \ds \\
                &= \mu \left[ 1 - \frac{\log \left(1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} \right].
    \end{align*}
    The total profits of the whole fringe is given by
    \begin{align*}
        \pi^t_F = \mu \left[ \frac{\log \left( 1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} - \frac{1}{N_P V_P + N_F V_F + 1} \right] - I_F(N_F).
    \end{align*}
\end{proposition}

@@

\begin{lemma}
    \label{lem:slope_at_eq}
    Let the conditions in \cref{ass:single_crossing} hold. Then for any $N_F^* > 0$ for which $\pi_F(N_P, N_F^*, N_C) = I_F(N_F)$, the partial derivative of fringe profits with respect to the number of fringe firms is smaller than the marginal investment cost:
    \begin{align*}
        \left. \frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_F} \right|_{N_F = N_F^*} < I_F'(N_F).
    \end{align*}
\end{lemma}
\begin{proof}[Proof of \cref{lem:slope_at_eq}]
    \cref{ass:single_crossing} states that at any $N_F \geq 0$, $\pi_F(N_P, N_F, N_C)$ is either concave or decreasing in $N_F$.
    In the remainder, let us denote partial derivatives as follows:
    \begin{align*}
        \partial_F \pi_F(N_P^*, N_F^*, N_C^*) \coloneqq \left. \frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_F} \right|_{N_P = N_P*, N_F = N_F^*, N_C = N_C^*}.
    \end{align*}

    Notice that the fact that $\pi_F$ is concave or decreasing in $N_F$ implies that if $\partial_F \pi_F(N_P, N_F', N_C)$ for some $N_F' \geq 0$, then $\partial_F \pi_F(N_P, N_F'', N_C) < \partial_F \pi_F(N_P, N_F', N_C)$ for any $\tilde{N_F} < \bar{N_F}$.

    Next, observe that if $\partial_F \pi_F(N_P, 0, N_C) < I_F'(0)$, then there is no equilibrium with $N_F > 0$.
    To show this, assume by contradiction that $\exists N_F^* > 0$ such that $\pi_F(N_P, N_F^*, N_C) = I_F(N_F^*)$.
    Then the mean value theorem implies that there is a $\bar{N}_F \in (0, N_F^*)$ such that $\partial_F \pi_F(N_P, \bar{N}_F, N_C) = I_F'(\bar{N_F}) \geq I_F'(0)$.
    However, this clearly cannot be the case as $\partial_F \pi_F(N_P, N_F, N_C) < I_F'(0)$ or $\pi_F(N_P, N_F, N_C) \leq 0$ for all $N_F > 0$.

    Now let $N_F^*$ be a positive number for which $f(N_P, N_F^*, N_C) = I_F(N_F^*)$.
    It is easy to see that $\partial \pi(N_P, N_F^*, N_C) < I_F'(N_F^*)$.
    The reason is that if it exists, then $\partial_F \pi_F(N_P, 0, N_C) > I_F'(0)$.
    Now if $\partial_F \pi_F(N_P, N_F, N_C) \geq I_F'(N_F) \forall N_F > 0$, then $f(N_P, N_F, N_F) > I_F(N_F)$, and the two functions do not intersect.
    Therefore, there must exist some $\bar{N}_F > 0$ for which $\partial_F \pi_F(N_P, \bar{N}_F, N_C) < I_F'(\bar{N}_F)$.
    This in turn implies that $\partial_F \pi_F(N_P, N_F, N_C) \leq \partial_F \pi_F(N_P, \bar{N}_F, N_C) < I_F'(\bar{N}_F) \leq I_F'(N_F)$ for all $N_F > \bar{N}_F$.
\end{proof}

\begin{proof}[Proof of \cref{prop:unique_equilibrium}]
    \Cref{lem:slope_at_eq} states that for any positive $N_F^*$ for which $\pi_F(N_P, N_F^*) - N_F I_F$, the partial derivative with respect to the number of fringe firms is negative.
    Now assume by contradiction that $\exists 0 < N_F^* < N_F^{**}$ such that $\pi_F(N_P, N_F^*) = I_F N_F^*$ and $\pi_F(N_P, N_F^{**}) = I_F N_F^{**}$.
    But then the mean value theorem implies that there is a $\bar{N}_F \in (N_F^*, N_F^{**})$ such that $\partial_F \pi_F(N_P, \bar{N}_F) = I_F$.
    This is a contradiction, as $\partial_F \pi_F(N_P, N_F) < I_F$ for all $N_F^* < N_F$.
\end{proof}

@@

\begin{proof}[Proof of \cref{cor:fringe_entry}]
    \Cref{prop:unique_equilibrium} establishes that if an equilibrium with $N_F > 0$ exists, it is unique.
    Use the implicit function theorem on the equation from \cref{ass:free_entry} to obtain
    \begin{align*}
        \frac{\partial N_F}{\partial N_P} = \frac{\frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_P}}{I_F'(N_F) - \frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F}}
    \end{align*}
    The derivative exists if the above expression is well-defined, i.e. $\frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F} \neq I_F$.
    Remember from \cref{prop:share_of_fringe} that the numerator of this expression is negative under the condition $\frac{\partial^2 f(N_P, N_F, N_C)}{\partial N_P \partial N_F}$.
    Now all we need to show to conclude the proof is that
    \begin{align*}
        \frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F} < I_F'(N_F),
    \end{align*}
    which is the statement of \cref{lem:slope_at_eq}.
\end{proof}

\begin{proof}[Proof of \cref{prop:aggregate_size_additive}]
    Use the implicit function theorem to get the equilibrium number of fringe firms as a function of the platform's product variety:
    \begin{align*}
        \frac{\partial N_F}{\partial N_P} = \frac{\frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_P}}{I_F'(N_F) - \frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F}}.
    \end{align*}
    Remember, that from \cref{lem:slope_at_eq}, and the assumption on the investment cost function we have that $\frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F} < I_F'(N_F)$.
    Then, substitute $f(N_P, N_F) = g(\alpha N_P + \beta N_P)$ into $\pi_F$ to get the following fringe profit function:
    \begin{align*}
        \pi_F(N_P, N_F, N_C) = \beta N_C N_F \int_0^1 w_s s g'(\alpha N_P + s \beta N_F) \ds.
    \end{align*}
    Differentiate it with respect to $N_P$ and $N_F$ and substitute into the first expression to obtain
    \begin{align*}
        \frac{\partial N_F}{\partial N_P} = \frac{
            \alpha \beta N_C N_P \int_0^1 w(s) g''(\alpha N_P + s \beta N_F) \ds
        }{
            \underbracket{I'_F(N_F) - \beta N_C \int_0^1 w(s) g'(\alpha N_P + s \beta N_F) \ds}_{(1)} - \underbracket{\beta^2 N_C N_F \int_0^1 w(s) s g''(\alpha N_P + s \beta N_F) \ds}_{(2)}.
        }
    \end{align*}
    From \cref{lem:slope_at_eq}, we know that the denominator of this expression is positive.
    Furthermore, the concavity of $g$ implies that expression (2) is also positive.
    Finally, from \cref{prop:share_of_fringe}, we have that the whole expression must be negative.

    First, let us show that (1) is non-negative, and, coupled with the fact that (2) is positive, omitting it increases the denominator in absolute value, thus making the whole expression larger.
    To see this, observe that the second part of (1) is just the per-unit fringe profit, i.e.
    \begin{align*}
        (1) = I_F'(N_F) - \pi_F(N_P, N_F, N_C) / N_F \geq 0 \Leftrightarrow N_F I_F'(N_F) - \pi_F(N_P, N_F, N_C) \leq 0.
    \end{align*}
    Next, use the convexity of $I_F$ and the definition of the equilibrium to obtain
    \begin{align*}
        N_F I_F'(N_F) - \pi_F(N_P, N_F, N_C) \leq I_F(N_F) - \pi_F(N_P, N_F, N_C) = 0,
    \end{align*}
    thus proving that (1) is non-negative.

    Next, observe that we can bound (2) from above using the fact that $s \in [0, 1]$:
    \begin{align*}
        (2) \leq \beta^2 N_C N_F \int_0^1 w(s) g''(\alpha N_P + s \beta N_F) \ds.
    \end{align*}
    For the same reason as before, it also bounds the whole expression from above.

    Putting it all together, we have that
    \begin{align*}
        \frac{\partial N_F}{\partial N_P} \leq \frac{\alpha \beta N_C N_P \int_0^1 w(s) g''(\alpha N_P + s \beta N_F) \ds}{\beta^2 N_C N_F \int_0^1 w(s) g''(\alpha N_P + s \beta N_F) \ds} = -\frac{\alpha}{\beta},
    \end{align*}
    which is the first statement of the proposition.
